\documentclass{article}
\usepackage[margin=1.0in]{geometry}
\usepackage[utf8]{inputenc}

\title{\LaTeX \ Setup for the Sublime Editor with Windows}
\author{Joseph Barton}
\date{}

\begin{document}

\maketitle

\begin{enumerate}
\item Install TeX Live https://www.tug.org/texlive/acquire.html. This will take some time to download.

\item Add TeX Live executables to your system path. It is in a folder similar to ``C:$ \backslash $texlive$ \backslash $2020$ \backslash $bin$ \backslash $win32''

\item In Sublime, go to Tools $\rightarrow$ Install Package Control to install the package controller.

\item Use Sublime's package control to install LaTeXTools package. In Sublime, go to ``Preferences $\rightarrow$ Package Control $\rightarrow$ Package Control: Install Package'' and scroll or search for LaTeXTools

\item Install the lightweight pdf reader SumatraPDF at https://www.sumatrapdfreader.org/download-free-pdf-viewer.html

\item It will likely install in your Admin folder and give you an error that it can't be opened.  It may be in ``C:$ \backslash $Users$ \backslash $.ARA-ADMIN$ \backslash $AppData$ \backslash $Local''. So move the SumatraPDF folder to ``C:$ \backslash $Program Files'' or somewhere else that is accessible.

\item Add the ``C:$ \backslash $Program Files$ \backslash $SumatraPDF'' (or whatever you chose) to your system path and restart your computer for the path changes to take affect.

\item Ensure setup is correct:
	\begin{itemize}
	\item Go to ``Preferences $\rightarrow$ Package Settings $\rightarrow$ LaTeXTools $\rightarrow$ Settings -- User'' and scroll to the Platform Settings (about line 209)
	\item Ensure the TeX distro is set to ``texlive''
	\item Go to ``Preferences $\rightarrow$ Package Settings $\rightarrow$ LaTeXTools $\rightarrow$ Check System''. The status of all essential programs should be labeled as ``available''.
	\end{itemize}

\item Now Create a .tex document (or just use this document) and press Ctrl+b to compile the file. Sumatra should pop up and show you the compiled document.

\item Install LaTex-cwl and LaTeXYZ with Sublime's package control just like we did above. These packages assist with autocompletion and syntax shortcuts. For reference:
	\begin{itemize}
	\item https://github.com/LaTeXing/LaTeX-cwl
	\item https://github.com/randy3k/LaTeXYZ
	\end{itemize}

\item Configure inverse search so you can compare a pdf object to an editor object easily.
	\begin{itemize}
	\item Compile a tex file so that SumatraPDF is displaying a tex document.
	\item In the SumatraPDF window, go to ``Settings $\rightarrow$ Options'' and in the inverse search section put the path to your sublime executible followed by ``\%f:\%l''
	\item For example: ``C:$ \backslash $Program Files$ \backslash $Sublime Text 3$ \backslash $sublime\_text.exe'' ``\%f:\%l''
	\item Now double clicking on a line in the pdf will automatically move the cursor to the corresponding line in Sublime.
	\end{itemize}

\item A comprehensive list of \LaTeX \ symbols can be found here:
	\begin{itemize}
	\item https://mirror.its.dal.ca/ctan/info/symbols/comprehensive/symbols-a4.pdf
	\end{itemize}
\end{enumerate}

\end{document}